Network segregation and Preferences for Redistribution across societies

### 2023-10-19 paper.Rmd
plot

ggplot(
  m1_df,
  aes(x = estimate, y = term, colour=term)) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_x_continuous(labels = label_percent()) +
  guides(color = "none") +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(
        axis.text.y.left = element_text(face = "bold",size = 12)
  )

>>>>

ggplot(
  m1_df,
  aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),size=1, width=0.2) +
  geom_point(shape=21, size=3, fill="white") +
  scale_y_discrete(labels=c("Working Class (V+VI+VII)",
                            "Intermediate class (III+IV)",  
                            "Class-based homogeneity")) +
  guides(color = "none") +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(
        axis.text.y.left = element_text(face = "plain",size = 12)
  )
